\documentclass[12pt, a4paper]{article}
\usepackage[margin=2.5cm]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{booktabs}

\pagestyle{fancy}
\fancyhf{}
\rhead{Trivia Game --- Auth Notes}
\lhead{Flask User System}
\cfoot{\thepage}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\lstset{
    basicstyle=\ttfamily\small,
    backgroundcolor=\color{gray!10},
    frame=single,
    breaklines=true,
    keywordstyle=\color{blue},
    stringstyle=\color{orange},
    commentstyle=\color{green!60!black},
    language=Python
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Flask User Authentication}}\\[0.5em]
    {\large Trivia Game --- Study Notes}\\[0.3em]
    {\small Educational Project}
\end{center}

\vspace{1em}
\hrule
\vspace{1.5em}

% ──────────────────────────────────────────────
\section{What Already Exists}

\begin{itemize}
    \item A \texttt{User} entry in the database
    \item Flask \texttt{session} --- already used for \texttt{current\_question} in the game
\end{itemize}

% ──────────────────────────────────────────────
\section{The 5 Steps for Users}

\subsection{Step 1 --- Register}
\begin{enumerate}
    \item Show a form: ask for username and password
    \item \textbf{Hash} the password --- never store it as plain text
    \item Save the new \texttt{User} record to the database
    \item Redirect the user to the Login page
\end{enumerate}

\subsection{Step 2 --- Login}
\begin{enumerate}
    \item Show a form: ask for username and password
    \item Look up the user in the DB by username
    \item Compare the submitted password against the stored hash
    \item If they match $\rightarrow$ save the user's id in the session:
\begin{lstlisting}
session["user_id"] = user.id
\end{lstlisting}
    \item Redirect to the game
\end{enumerate}

\subsection{Step 3 --- Logout}
\begin{enumerate}
    \item Remove the user id from the session:
\begin{lstlisting}
session.pop("user_id", None)
\end{lstlisting}
    \item Redirect to the home page
\end{enumerate}

\subsection{Step 4 --- Who is playing right now?}
\begin{enumerate}
    \item Check the session at the top of any route:
\begin{lstlisting}
user_id = session.get("user_id")
if user_id:
    # logged in user
else:
    # guest
\end{lstlisting}
\end{enumerate}

\subsection{Step 5 --- Protect a route (optional, for later)}
\begin{enumerate}
    \item If a page requires login, check at the top of the route
    \item If not logged in $\rightarrow$ redirect to login page
\end{enumerate}

% ──────────────────────────────────────────────
\section{The Name Entry Flow (Geography Game)}

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{User types} & \textbf{Condition} & \textbf{Action} \\
\midrule
\texttt{db}         & name == ``db''     & Ask: ``Do you want to login?'' \\
                    & $\rightarrow$ Yes  & Redirect to \texttt{/login} \\
                    & $\rightarrow$ No   & Back to name entry \\
\midrule
anything else       & name != ``db''     & Ask: ``Guest or Register?'' \\
                    & $\rightarrow$ Guest    & Save name to session, start game \\
                    & $\rightarrow$ Register & Redirect to \texttt{/register} \\
\bottomrule
\end{tabular}
\end{center}

% ──────────────────────────────────────────────
\section{Files to Create or Edit}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{File} & \textbf{Purpose} \\
\midrule
\texttt{app/models.py}             & Add \texttt{User} model (username, password hash) \\
\texttt{app/auth.py}               & Register, Login, Logout routes \\
\texttt{templates/register.html}   & Registration form \\
\texttt{templates/login.html}      & Login form \\
\texttt{geography/\_\_init\_\_.py} & Name entry logic before the game starts \\
\texttt{templates/geography.html}  & Name entry / login prompt / guest screens \\
\bottomrule
\end{tabular}
\end{center}

% ──────────────────────────────────────────────
\section{Key Concepts to Remember}

\begin{description}
    \item[Hashing] A one-way transformation of a password. You can never reverse it.
    Use \texttt{werkzeug.security}: \\
    \texttt{generate\_password\_hash()} to save, \\
    \texttt{check\_password\_hash()} to verify.

    \item[Session] A small dictionary stored securely in the browser cookie.
    Flask signs it with a \texttt{SECRET\_KEY} so the user cannot tamper with it.

    \item[Blueprint] A way to split routes into separate files.
    The geography game is already a Blueprint. Auth will be another one.

    \item[Redirect] After login or register, always redirect --- never render directly.
    This prevents the browser from re-submitting the form on refresh.
\end{description}

\vspace{2em}
\hrule
\vspace{0.5em}
{\small \textit{Next step: open \texttt{app/models.py} and check the User model before writing any route.}}

\end{document}
